### 2020-11-05 submission/manuscript.Rmd
Acknowledgements section
Incorporate citations into Table 1

**Datasets.** I collected `r nrow(table_1)` publicly available datasets that used the Illumina MiSeq platform to sequence the V4 region of the 16S rRNA gene from a variety of environments (Table 1). To insure the highest possible data quality, datasets were limited to those where the 500 cycle v2 MiSeq chemistry was used to sequence the amplicons. The paired 250 nt reads resulted in near complete 2-fold sequencing coverage of every nucleotide in the ca. 250 nt-long region. This region and sequencing platform were selected because previous work has shown that a standard data analysis pipeline in mothur results in a sequencing error rate below 0.02% [@Kozich2013]. All sequence data were obtained from the Sequence Read Archive and processed using a standard mothur-based sequencing pipeline that resulted in ASVs as generated by the pre.cluster algorithm [@Kozich2013; @Schloss2009]. After removing poor quality and chimeric ASVs and samples that had uncharacteristically low number of sequences for the dataset, these datasets included between `r oxford_comma(n_sample_range)` samples (Figure S1). The median number of sequences for each dataset ranged between `r oxford_comma(n_med_sequence_range)` (Table 1). Strikingly, aside from the relatively small `r oxford_comma(low_fold_samples)` datasets, the difference between the sample with the fewest sequences and the sample with the most sequences for each dataset varied by between `r oxford_comma(high_fold_range, digits=1)`-fold (Table 1).

@@

* sequencing pipeline description

@@

@@

```{r}
table_1 %>%
  arrange(nice_name) %>%
  mutate(total_seqs=format(total_seqs, big.mark=",", trim=TRUE),
    median=format(as.integer(median), big.mark=",", trim=TRUE),
    min=format(min, big.mark=",", trim=TRUE),
    max=format(max, big.mark=",", trim=TRUE),
    range = glue("{min}-{max}"),
    n_samples = n_samples,
    fold_difference = round(fold_difference, 1)) %>%
  select(nice_name, n_samples, total_seqs, median, range, fold_difference) %>%
  kable("latex", booktabs=TRUE, escape=F, align="lrrrrr", linesep="",
		col.names = linebreak(c("Study", "Samples", "Total\nsequences", "Median\nsequences",
			"Range of\nsequences", "Fold-difference\nbetween largest\nand smallest sample"), align="c")
	) %>%
	row_spec(0, bold=T)
```

>>>>

**Datasets.** I collected `r nrow(table_1)` publicly available datasets that used the Illumina MiSeq platform to sequence the V4 region of the 16S rRNA gene from a variety of environments (Table 1). To insure the highest possible data quality, datasets were limited to those where the 500 cycle v2 MiSeq chemistry was used to sequence the amplicons. The paired 250 nt reads resulted in near complete 2-fold sequencing coverage of every nucleotide in the ca. 250 nt-long region. This region and sequencing platform were selected because previous work has shown that a standard data analysis pipeline in mothur results in a sequencing error rate below 0.02% [@Kozich2013]. All sequence data were obtained from the Sequence Read Archive (SRA) and processed using a standard mothur-based sequencing pipeline that resulted in ASVs as generated by the pre.cluster algorithm [@Kozich2013; @Schloss2009]. After removing poor quality and chimeric ASVs and samples that had uncharacteristically low number of sequences for the dataset, these datasets included between `r oxford_comma(n_sample_range)` samples (Figure S1). The median number of sequences for each dataset ranged between `r oxford_comma(n_med_sequence_range)` (Table 1). Strikingly, aside from the relatively small `r oxford_comma(low_fold_samples)` datasets, the difference between the sample with the fewest sequences and the sample with the most sequences for each dataset varied by between `r oxford_comma(high_fold_range, digits=1)`-fold (Table 1).

@@

Datasets were selected because they sequenced the V4 region of the 16S rRNA gene using Illumina's MiSeq platform using the v2 chemistry with paired 250 nt reads. I identified 12 datasets that satisfied these criteria and downloaded the data directly from the SRA (Table 1 and Figure S1).

* Used the mothur pipeline to
  - Assembly of paired 250 nt reads
*

@@

I endebted to the researchers who developed the 12 datasets used in this study for depositing their sequence data into the Sequence Read Archive. This work was supported in part by funding from the National Institutes of Health (U01AI124255, P30DK034933, R01CA215574).

@@

\small

```{r}
table_1 %>%
  arrange(nice_name) %>%
  mutate(
    nice_name = glue("{nice_name} {reference}"),
    total_seqs=format(total_seqs, big.mark=",", trim=TRUE),
    median=format(as.integer(median), big.mark=",", trim=TRUE),
    min=format(min, big.mark=",", trim=TRUE),
    max=format(max, big.mark=",", trim=TRUE),
    range = glue("{min}-{max}"),
    n_samples = n_samples,
    fold_difference = round(fold_difference, 1)) %>%
  select(nice_name, n_samples, total_seqs, median, range, fold_difference, sra_study) %>%
  kableExtra::kable(format="markdown", booktabs=TRUE, escape=F, align="lrrrrr",
    linesep="",
		col.names = linebreak(
      c(
        "\\textbf{Study (Ref)}",
        "\\textbf{Samples}",
        "\\textbf{Total}\n\\textbf{sequences}",
        "\\textbf{Median}\n\\textbf{sequences}",
        "\\textbf{Range of}\n\\textbf{sequences}",
        "\\textbf{Fold-difference}\n\\textbf{between largest}\n\\textbf{and smallest sample}",
        "\\textbf{SRA study}\n\\textbf{accession}"
      ),
      align="c")
	)
```
\normalsize

### 2020-11-05 submission/manuscript.tex
Acknowledgements section
Incorporate citations into Table 1

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
  \usepackage{amssymb}
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{setspace}
\doublespacing
\usepackage[left]{lineno}
\linenumbers
\modulolinenumbers
\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
\usepackage[T1]{fontenc}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\textbf{Datasets.} I collected 12 publicly available datasets that used
the Illumina MiSeq platform to sequence the V4 region of the 16S rRNA
gene from a variety of environments (Table 1). To insure the highest
possible data quality, datasets were limited to those where the 500
cycle v2 MiSeq chemistry was used to sequence the amplicons. The paired
250 nt reads resulted in near complete 2-fold sequencing coverage of
every nucleotide in the ca. 250 nt-long region. This region and
sequencing platform were selected because previous work has shown that a
standard data analysis pipeline in mothur results in a sequencing error
rate below 0.02\% (1). All sequence data were obtained from the Sequence
Read Archive and processed using a standard mothur-based sequencing
pipeline that resulted in ASVs as generated by the pre.cluster algorithm
(1, 2). After removing poor quality and chimeric ASVs and samples that
had uncharacteristically low number of sequences for the dataset, these
datasets included between 7 and 490 samples (Figure S1). The median
number of sequences for each dataset ranged between 6,477 and 193,464
(Table 1). Strikingly, aside from the relatively small marine and soil
datasets, the difference between the sample with the fewest sequences
and the sample with the most sequences for each dataset varied by
between 7.4 and 96.6-fold (Table 1).

@@

\begin{itemize}
\tightlist
\item
  sequencing pipeline description
\end{itemize}

@@

@@

\begin{tabular}{lrrrrr}
\toprule
\textbf{Study} & \textbf{Samples} & \textbf{\makecell[c]{Total\\sequences}} & \textbf{\makecell[c]{Median\\sequences}} & \textbf{\makecell[c]{Range of\\sequences}} & \textbf{\makecell[c]{Fold-difference\\between largest\\and smallest sample}}\\
\midrule
Bioethanol & 95 & 3,972,943 & 16,015 & 3,688-356,136 & 96.6\\
Human & 490 & 20,909,768 & 32,505 & 10,523-430,415 & 40.9\\
Lake & 52 & 3,169,868 & 69,041 & 15,347-112,871 & 7.4\\
Marine & 7 & 1,391,396 & 193,464 & 133,516-254,060 & 1.9\\
Mice & 348 & 2,813,747 & 6,477 & 1,804-30,565 & 16.9\\
Peromyscus & 111 & 1,555,545 & 12,446 & 4,464-33,644 & 7.5\\
Rainforest & 69 & 946,295 & 11,561 & 4,932-37,767 & 7.7\\
Rice & 490 & 22,591,168 & 43,216 & 2,776-193,464 & 69.7\\
Seagrass & 286 & 4,130,454 & 13,567 & 1,803-45,191 & 25.1\\
Sediment & 58 & 1,154,174 & 17,584 & 7,685-68,321 & 8.9\\
Soil & 18 & 956,656 & 51,844 & 47,806-59,956 & 1.3\\
Stream & 201 & 21,162,574 & 90,159 & 9,175-390,964 & 42.6\\
\bottomrule
\end{tabular}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
  \usepackage{amssymb}
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1.0in]{geometry}
\usepackage{longtable,booktabs}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{setspace}
\doublespacing
\usepackage[left]{lineno}
\linenumbers
\modulolinenumbers
\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
\usepackage[T1]{fontenc}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

\textbf{Datasets.} I collected 12 publicly available datasets that used
the Illumina MiSeq platform to sequence the V4 region of the 16S rRNA
gene from a variety of environments (Table 1). To insure the highest
possible data quality, datasets were limited to those where the 500
cycle v2 MiSeq chemistry was used to sequence the amplicons. The paired
250 nt reads resulted in near complete 2-fold sequencing coverage of
every nucleotide in the ca. 250 nt-long region. This region and
sequencing platform were selected because previous work has shown that a
standard data analysis pipeline in mothur results in a sequencing error
rate below 0.02\% (1). All sequence data were obtained from the Sequence
Read Archive (SRA) and processed using a standard mothur-based
sequencing pipeline that resulted in ASVs as generated by the
pre.cluster algorithm (1, 2). After removing poor quality and chimeric
ASVs and samples that had uncharacteristically low number of sequences
for the dataset, these datasets included between 7 and 490 samples
(Figure S1). The median number of sequences for each dataset ranged
between 6,477 and 193,464 (Table 1). Strikingly, aside from the
relatively small marine and soil datasets, the difference between the
sample with the fewest sequences and the sample with the most sequences
for each dataset varied by between 7.4 and 96.6-fold (Table 1).

@@

Datasets were selected because they sequenced the V4 region of the 16S
rRNA gene using Illumina's MiSeq platform using the v2 chemistry with
paired 250 nt reads. I identified 12 datasets that satisfied these
criteria and downloaded the data directly from the SRA (Table 1 and
Figure S1).

\begin{itemize}
\tightlist
\item
  Used the mothur pipeline to

  \begin{itemize}
  \tightlist
  \item
    Assembly of paired 250 nt reads
  \end{itemize}
\item
\end{itemize}

@@

\leavevmode\hypertarget{ref-Li2015}{}%
\CSLLeftMargin{15. }
\CSLRightInline{\textbf{Li Q}, \textbf{Heist EP}, \textbf{Moe LA}. 2015.
Bacterial community structure and dynamics during corn-based bioethanol
fermentation. Microbial Ecology \textbf{71}:409--421.
doi:\href{https://doi.org/10.1007/s00248-015-0673-9}{10.1007/s00248-015-0673-9}.}

\leavevmode\hypertarget{ref-Baxter2016}{}%
\CSLLeftMargin{16. }
\CSLRightInline{\textbf{Baxter NT}, \textbf{Ruffin MT}, \textbf{Rogers
MAM}, \textbf{Schloss PD}. 2016. Microbiota-based model improves the
sensitivity of fecal immunochemical test for detecting colonic lesions.
Genome Medicine \textbf{8}.
doi:\href{https://doi.org/10.1186/s13073-016-0290-3}{10.1186/s13073-016-0290-3}.}

\leavevmode\hypertarget{ref-Beall2015}{}%
\CSLLeftMargin{17. }
\CSLRightInline{\textbf{Beall BFN}, \textbf{Twiss MR}, \textbf{Smith
DE}, \textbf{Oyserman BO}, \textbf{Rozmarynowycz MJ}, \textbf{Binding
CE}, \textbf{Bourbonniere RA}, \textbf{Bullerjahn GS}, \textbf{Palmer
ME}, \textbf{Reavie ED}, \textbf{Waters LMK}, \textbf{Woityra LWC},
\textbf{McKay RML}. 2015. Ice cover extent drives phytoplankton and
bacterial community structure in a large north-temperate lake:
Implications for a warming climate. Environmental Microbiology
\textbf{18}:1704--1719.
doi:\href{https://doi.org/10.1111/1462-2920.12819}{10.1111/1462-2920.12819}.}

\leavevmode\hypertarget{ref-Henson2016}{}%
\CSLLeftMargin{18. }
\CSLRightInline{\textbf{Henson MW}, \textbf{Pitre DM}, \textbf{Weckhorst
JL}, \textbf{Lanclos VC}, \textbf{Webber AT}, \textbf{Thrash JC}. 2016.
Artificial seawater media facilitate cultivating members of the
microbial majority from the gulf of mexico. {mSphere} \textbf{1}.
doi:\href{https://doi.org/10.1128/msphere.00028-16}{10.1128/msphere.00028-16}.}

\leavevmode\hypertarget{ref-Baxter2014}{}%
\CSLLeftMargin{19. }
\CSLRightInline{\textbf{Baxter NT}, \textbf{Wan JJ}, \textbf{Schubert
AM}, \textbf{Jenior ML}, \textbf{Myers P}, \textbf{Schloss PD}. 2014.
Intra- and interindividual variations mask interspecies variation in the
microbiota of sympatric peromyscus populations. Applied and
Environmental Microbiology \textbf{81}:396--404.
doi:\href{https://doi.org/10.1128/aem.02303-14}{10.1128/aem.02303-14}.}

\leavevmode\hypertarget{ref-LevyBooth2018}{}%
\CSLLeftMargin{20. }
\CSLRightInline{\textbf{Levy-Booth DJ}, \textbf{Giesbrecht IJW},
\textbf{Kellogg CTE}, \textbf{Heger TJ}, \textbf{D'Amore DV},
\textbf{Keeling PJ}, \textbf{Hallam SJ}, \textbf{Mohn WW}. 2018.
Seasonal and ecohydrological regulation of active microbial populations
involved in {DOC}, {CO}2, and {CH}4 fluxes in temperate rainforest soil.
The {ISME} Journal \textbf{13}:950--963.
doi:\href{https://doi.org/10.1038/s41396-018-0334-3}{10.1038/s41396-018-0334-3}.}

\leavevmode\hypertarget{ref-Edwards2015}{}%
\CSLLeftMargin{21. }
\CSLRightInline{\textbf{Edwards J}, \textbf{Johnson C},
\textbf{Santos-Medellín C}, \textbf{Lurie E}, \textbf{Podishetty NK},
\textbf{Bhatnagar S}, \textbf{Eisen JA}, \textbf{Sundaresan V}. 2015.
Structure, variation, and assembly of the root-associated microbiomes of
rice. Proceedings of the National Academy of Sciences
\textbf{112}:E911--E920.
doi:\href{https://doi.org/10.1073/pnas.1414592112}{10.1073/pnas.1414592112}.}

\leavevmode\hypertarget{ref-Ettinger2017}{}%
\CSLLeftMargin{22. }
\CSLRightInline{\textbf{Ettinger CL}, \textbf{Williams SL},
\textbf{Abbott JM}, \textbf{Stachowicz JJ}, \textbf{Eisen JA}. 2017.
Microbiome succession during ammonification in eelgrass bed sediments.
{PeerJ} \textbf{5}:e3674.
doi:\href{https://doi.org/10.7717/peerj.3674}{10.7717/peerj.3674}.}

\leavevmode\hypertarget{ref-Graw2018}{}%
\CSLLeftMargin{23. }
\CSLRightInline{\textbf{Graw MF}, \textbf{DAngelo G}, \textbf{Borchers
M}, \textbf{Thurber AR}, \textbf{Johnson JE}, \textbf{Zhang C},
\textbf{Liu H}, \textbf{Colwell FS}. 2018. Energy gradients structure
microbial communities across sediment horizons in deep marine sediments
of the south china sea. Frontiers in Microbiology \textbf{9}.
doi:\href{https://doi.org/10.3389/fmicb.2018.00729}{10.3389/fmicb.2018.00729}.}

\leavevmode\hypertarget{ref-Johnston2016}{}%
\CSLLeftMargin{24. }
\CSLRightInline{\textbf{Johnston ER}, \textbf{Rodriguez-R LM},
\textbf{Luo C}, \textbf{Yuan MM}, \textbf{Wu L}, \textbf{He Z},
\textbf{Schuur EAG}, \textbf{Luo Y}, \textbf{Tiedje JM}, \textbf{Zhou
J}, \textbf{Konstantinidis KT}. 2016. Metagenomics reveals pervasive
bacterial populations and reduced community diversity across the alaska
tundra ecosystem. Frontiers in Microbiology \textbf{7}.
doi:\href{https://doi.org/10.3389/fmicb.2016.00579}{10.3389/fmicb.2016.00579}.}

\leavevmode\hypertarget{ref-Hassell2018}{}%
\CSLLeftMargin{25. }
\CSLRightInline{\textbf{Hassell N}, \textbf{Tinker KA}, \textbf{Moore
T}, \textbf{Ottesen EA}. 2018. Temporal and spatial dynamics in
microbial community composition within a temperate stream network.
Environmental Microbiology \textbf{20}:3560--3572.
doi:\href{https://doi.org/10.1111/1462-2920.14311}{10.1111/1462-2920.14311}.}

@@

\small

\begin{longtable}[]{@{}lrrrrrl@{}}
\toprule
\textbf{Study (Ref)} & \textbf{Samples} &
\makecell[c]{\textbf{Total}\\\textbf{sequences}} &
\makecell[c]{\textbf{Median}\\\textbf{sequences}} &
\makecell[c]{\textbf{Range of}\\\textbf{sequences}} &
\makecell[c]{\textbf{Fold-difference}\\\textbf{between largest}\\\textbf{and smallest sample}}
& \makecell[c]{\textbf{SRA study}\\\textbf{accession}}\tabularnewline
\midrule
\endhead
Bioethanol (15) & 95 & 3,972,943 & 16,015 & 3,688-356,136 & 96.6 &
SRP055545\tabularnewline
Human (16) & 490 & 20,909,768 & 32,505 & 10,523-430,415 & 40.9 &
SRP062005\tabularnewline
Lake (17) & 52 & 3,169,868 & 69,041 & 15,347-112,871 & 7.4 &
SRP050963\tabularnewline
Marine (18) & 7 & 1,391,396 & 193,464 & 133,516-254,060 & 1.9 &
SRP068101\tabularnewline
Mice (1) & 348 & 2,813,747 & 6,477 & 1,804-30,565 & 16.9 &
SRP192323\tabularnewline
Peromyscus (19) & 111 & 1,555,545 & 12,446 & 4,464-33,644 & 7.5 &
SRP044050\tabularnewline
Rainforest (20) & 69 & 946,295 & 11,561 & 4,932-37,767 & 7.7 &
ERP023747\tabularnewline
Rice (21) & 490 & 22,591,168 & 43,216 & 2,776-193,464 & 69.7 &
SRP044745\tabularnewline
Seagrass (22) & 286 & 4,130,454 & 13,567 & 1,803-45,191 & 25.1 &
SRP092441\tabularnewline
Sediment (23) & 58 & 1,154,174 & 17,584 & 7,685-68,321 & 8.9 &
SRP097192\tabularnewline
Soil (24) & 18 & 956,656 & 51,844 & 47,806-59,956 & 1.3 &
ERP012016\tabularnewline
Stream (25) & 201 & 21,162,574 & 90,159 & 9,175-390,964 & 42.6 &
SRP075852\tabularnewline
\bottomrule
\end{longtable}

\normalsize
